# epiworldRShiny: An RShiny Application for the epiworldR Package

<!-- badges: start -->

<!-- badges: end -->

To run this ShinyApp, you need to type the following:

```{r}
epiworldRShiny()
```

This R package provides a user-friendly application for [epiworldR](https://github.com/UofUEpiBio/epiworldR){target="_blank"}, a wrapper of the C++ library [epiworld](https://github.com/UofUEpiBio/epiworld){target="_blank"}. It provides a general framework for modeling disease transmission using [agent-based models](https://en.wikipedia.org/w/index.php?title=Agent-based_model&oldid=1153634802){target="_blank"}. Some of the main features include:

-   Fast simulation with an average of 30 million agents/day per second.
-   One model can include multiple diseases.
-   Policies (tools) can be multiple and user-defined.
-   Transmission can be a function of agents’ features.
-   Out-of-the-box parallelization for multiple simulations.

From package description of [epiworldR](https://github.com/UofUEpiBio/epiworldR){target="_blank"}

> A flexible framework for Agent-Based Models (ABM), the epiworldR package provides methods for prototyping disease outbreaks and transmission models using a C++ backend, making it very fast. It supports multiple epidemiological models, including the Susceptible-Infected-Susceptible (SIS), Susceptible-Infected-Removed (SIR), Susceptible-Exposed-Infected-Removed (SEIR), and others, involving arbitrary mitigation policies and multiple-disease models. Users can specify infectiousness/susceptibility rates as a function of agents’ features, providing great complexity for the model dynamics. Furthermore, epiworldR is ideal for simulation studies featuring large populations.

## Installation

You can install the development version of epiworldRShiny from [GitHub](https://github.com/) with:

```{r}
devtools::install_github("UofUEpiBio/epiworldRShiny")
```

Or from CRAN

```{r}
install.packages("epiworldRShiny")
```
